Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
Remove comment
Comment a comment

\begin{quote}
    sol: We e.g. say ill-behaved Monoid instance.  So is
    ``behavior'' really a ``bad'' word?  But I agree that some people in
    the community might associated it with something imperative.

    kazu: ``behavior'' sounded strange at least to me at the first time.
    We alreay supported this word with typeclassopedia. So, I think
    this paragraph is completed. Should we replace ``is associated'' with
    ``might be associated''?

    sol: @kazu, this was primarily meant for @mkl as reference.

    One might also argue that ``should'' is not very mathematical, but
    it is common language when we talk about mathematics.  E.g. Brent
    Yorgey uses both ``should'' and ``behave'' a lot in the
    Typeclassopedia (e.g. ``\ldots {\tt Alternative} should satisfy
    the monoid laws\ldots'')
\end{quote}

@@

\begin{quote}
    sol: I think you can have several files with tests, but you have
    to combine the test suites manually.
\end{quote}

>>>>

%\begin{quote}
%    sol: We e.g. say ill-behaved Monoid instance.  So is
%    ``behavior'' really a ``bad'' word?  But I agree that some people in
%    the community might associated it with something imperative.
%
%    kazu: ``behavior'' sounded strange at least to me at the first time.
%    We alreay supported this word with typeclassopedia. So, I think
%    this paragraph is completed. Should we replace ``is associated'' with
%    ``might be associated''?
%
%    sol: @kazu, this was primarily meant for @mkl as reference.
%
%    One might also argue that ``should'' is not very mathematical, but
%    it is common language when we talk about mathematics.  E.g. Brent
%    Yorgey uses both ``should'' and ``behave'' a lot in the
%    Typeclassopedia (e.g. ``\ldots {\tt Alternative} should satisfy
%    the monoid laws\ldots'')
%\end{quote}

@@
